---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DAIVEtools

<!-- badges: start -->
<!-- badges: end -->

The goal of DAIVEtools is to support Decision Analysis for Intervention Value Efficiency (DAIVE) by providing R functions to easily format data, visualize results, and identify frontiers of efficiency for factorial optimization trial data.

## Installation

You can install the development version of DAIVEtools from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("setheaton/DAIVEtools")
```

## Example

This is a basic example which shows how DAIVEtools can format posterior draws data into a table of expected value:

```{r valuestable, warning=FALSE, message=FALSE}
library(DAIVEtools)

## combine draws dataframes into a list object
draws <- list(gpaDraws, actDraws)

## define vectors of components and outcomes labels
components <- c("A", "B", "C")
outcomes <- c("GPA", "ACT")

## generate a daive_grid object with expected values of alternatives
g <- DAIVEtools::daive_grid(draws, 
                            outcomes, 
                            components, 
                            costs=c(70, 60, 20))
get_table(g)
```

Grid objects can be updated to easily combine outcomes with value functions and identify frontiers of efficiency:

```{r frontier}
## define weights for outcomes
weights <- c(100/160, 60/160)

## calculate a value function as a weighted sum
g <- DAIVEtools::update_weights(g, weights)
summary(g)
```

Grid objects can also easily be used to visualize frontiers of efficiency:

```{r frontier_plot}
DAIVEtools::frontier_plot(g, static=TRUE)
```

And to visualize intervals for expected values:

```{r ev_plot, warning=FALSE, message=FALSE}
DAIVEtools::ev_plot(g)
```
