---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DAIVEtools

<!-- badges: start -->
<!-- badges: end -->

The goal of DAIVEtools is to support Decision Analysis for Intervention Value Efficiency (DAIVE) by providing methods easily format data, visualize results, and identify frontiers of efficiency for factorial optimization trial data.

## Installation

You can install the development version of DAIVEtools from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("setheaton/DAIVEtools")
```

## Example

This is a basic example which shows how DAIVEtools can format posterior draws data into a table of expected value:

```{r valuestable, warning=FALSE, message=FALSE}
library(DAIVEtools)

## combine draws dataframes into a list object
draws <- list(gpaDraws, actDraws)

## define vectors of components and outcomes labels
components <- c("A", "B", "C")
outcomes <- c("GPA", "ACT")

## generate a frame with effects codes
codes <- DAIVEtools::get_codes(components)

## generate a value summary table
expectedValue <- DAIVEtools::values_table(draws, outcomes, components, codes)
expectedValue
```

Values tables can be used to easily combine outcomes with value functions and identify frontiers of efficiency:

```{r frontier}
## define weights for outcomes
weights <- c(100/160, 60/160)

## calculate a value function as a weighted sum
expectedValue$valueFunc <- DAIVEtools::weight_outcomes(expectedValue,
                                                    c("GPA.scale", "ACT.scale"), 
                                                    weights)
expectedValue

## calculate alternative costs using component costs
expectedValue$cost <- rowSums(expand.grid(A=c(0, 70), B=c(0, 60), C=c(0,20)))

## identify a frontier
DAIVEtools::frontier(expectedValue, "valueFunc", "cost")
```

Values tables can also be used to easily visualize frontiers of efficiency:

```{r plot}
DAIVEtools::DAIVE_plot(expectedValue, "valueFunc", "cost", 
                       outs=c("Scaled GPA", "Scaled ACT"), weights=weights, 
                       static=TRUE)
```
